
\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{graphicx}
\graphicspath{{images/}{../images/}}
\usepackage{subfiles}
\usepackage{blindtext}
\usepackage{amsmath,amsfonts,amssymb,amsthm,epsfig,epstopdf,titling,url,array, tikz,tkz-berge,  calrsfs}
\usepackage{tkz-graph}
\usepackage{algorithm, float}
\usepackage[noend]{algpseudocode}
 
\title{Matroids And their Graphs}
\author{o.mcdonnell4@nuigalway.ie }
\date{April 2018}

\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem*{cor}{Corollary}
\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{exmp}[thm]{Example}
\theoremstyle{remark}
\newtheorem*{rem}{Remark}
\newtheorem*{note}{Note}
\newenvironment{rcases}
  {\left.\begin{aligned}}
  {\end{aligned}\right\rbrace}
\newcounter{excercise}
\newcounter{solution}
\newcounter{Question}
\newcommand\Excercise{%
  \textbf{Excercise:}~%
  \setcounter{solution}{0}%
}
\newcommand\Problem{%
  \textbf{Problem:}~%
}
\newcommand\TheSolution{%
  \textbf{Solution:}\\%
}
\newcommand\Question{%
    \textbf{Question:}~%
    \setcounter{Question}{0}%
}
\newcommand\Notation{%
  \textbf{Notation:}~%
}
\newcommand\Proof{%
    \textbf{Proof:}~%
}
\GraphInit[vstyle = Shade]
\tikzset{
  LabelStyle/.style = { rectangle, rounded corners, draw, minimum height = 2em,
                        minimum width = 2em, fill = white!50,
                        text = red, font = \Large\bfseries },
  VertexStyle/.append style = { inner sep=4pt,
                                font = \bfseries},
  EdgeStyle/.append style = { } }
\thispagestyle{empty}
  
\begin{document}
 
\maketitle
 
\subfile{sections/abstract}

\section{Introduction}
\subfile{sections/introduction}
\subfile{sections/intro2}
\subfile{sections/intro3}
\subfile{sections/intro4}

\section{Cryptomorphisms}
\subfile{sections/char1}
\subfile{sections/char12}
\subfile{sections/char2}
\subfile{sections/char21}

\section{Graph Theory}
\subfile{sections/g1}

\section{Greedy Algorithm}
\subfile{sections/algo1}

\section{Optimization Problems}
\subfile{sections/algo2}
\subfile{sections/opt1}
\subfile{sections/opt3}
\subfile{sections/opt2}

\section{Other Optimizable set-systems}
\subfile{sections/gre1}

\section{Appendix}
\subfile{sections/algo3}

\begin{thebibliography}{}
\bibitem{ox_book}
    Oxley, James (1992), Matroid Theory, Oxford: Oxford University Press, ISBN 0-19-853563-5, MR 1207587, Zbl 0784.05002.
\bibitem{ox_paper}
    James Oxley : What is a matroid? https://www.math.lsu.edu/~oxley/survey4.pdf
\bibitem{jungnickel}
	Jungnickel, Dieter (2013), Graphs,Networks and Algorithms, Springer-Verlag Berlin Heidelberg, ISBN 978-3-642-32277-8 
\bibitem{whitney}
	Whitney, Hassler. “On the Abstract Properties of Linear Dependence.” American Journal of Mathematics, vol. 57, no. 3, 1935, pp. 		509–533. JSTOR, JSTOR, www.jstor.org/stable/2371182.
\bibitem{maclane_saunders}
	MacLane, Saunders. “Some Interpretations of Abstract Linear Dependence in Terms of Projective Geometry.” American Journal of 			Mathematics, vol. 58, no. 1, 1936, pp. 236–240. JSTOR, JSTOR, www.jstor.org/stable/2371070.
\bibitem{kruskal}
	Kruskal, Joseph B., Jr. On the shortest spanning subtree of a graph and the traveling salesman problem. Proc. Amer. Math. Soc. 7 	(1956), 48–50. 
\bibitem{boruvka}
	Otakar Borůvka, On a minimal problem, Práce Moravské Pridovedecké Spolecnosti, vol. 3, 1926. 
\bibitem{welsh}
	Dominic J.A. Welsh, A bound for the number of matroids, Journal of Combinatorial Theory, Volume 6, Issue 3, 1969, Pages 313-316, 	ISSN 0021-9800, https://doi.org/10.1016/S0021-9800(69)80094-3. (http://www.sciencedirect.com/science/article/pii/				S0021980069800943)
\bibitem{greedoids}
	Bjørner, A., Ziegler, G.M.: Introduction to greedoids. In: White, N.(ed) Matroid Applications, pp. 284–357. Cambridge University 	Press, Cambridge (1992)
\bibitem{kortez__lovasz}
	Korte and Lovasz (1984) Korte, B., Lovasz, L.: Greedoids and linear objective functions. SIAM J. Algebr. Discr. Math.5, 229– 			238 (1984)
\bibitem{bryant_brooksbank}
	Bryant,  V.,  Brooksbank,  P.:  Greedy  algorithm  compatibility  and heavy-set structures. Europ. J. Comb. 13 , 81–86 (1992)
\end{thebibliography}


\end{document}

